\documentclass[11pt,letterpaper,roman]{moderncv}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage[disable]{todonotes}
\usepackage{lastpage}

\moderncvstyle{classic}
\moderncvcolor{black}

\pagenumbering{arabic}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

\newcommand{\tabbed}{\setlength{\itemindent}{1em}}

\name{Hunter}{Damron}
\title{Curriculum Vit\ae}
\address{4569 Edgeland Road}{Edgemoor, SC}{}
\phone[mobile]{+1~(803)~448~4411}
\email{hdamron@email.sc.edu}
%\homepage{cse.sc.edu/~hdamron}
\social[github]{github.com/hdamron17}
\extrainfo{Citizen of U.S.A.}

\begin{document}
\makecvtitle{}

\todo[inline]{TODO\@: \\
	Check names and improve wording for all awards in education section
}

\section{Education}
\cventry{2017--present}{BS, Computer Engineering and Mathematics Double Major}{University of South Carolina Honors College}{Columbia, SC}{}{}
\cvitem{\small Current GPA:}{4.0/4.0}
\cvitem{\small Honors:}{\begin{itemize}
		\item Carolina Scholarship -- Awarded by the University of South Carolina to 20 students for academic and extracurricular leadership and excellence in high school.
		\item ICPC College of Charleston Competition Division I Third Place -- Computer science problem solving competition in teams of three.
		\item President's List Fall 2017 -- Awarded for average 4.00 GPA earned on a semester of at least 12 credit hours.
	\end{itemize}}
\cventry{2015--2017}{High School Diploma}{SC Governor's School for Science and Mathematics}{Hartsville, SC}{}{}
\cvitem{\small GPA:}{4.0/4.0}
\cvitem{\small Honors:}{\begin{itemize}
		\item University of Rochester Bausch and Lomb Honorary Science Award -- Awarded for excellence in rigorous science courseload.
		\item Senior Computer Science Award -- Awarded to one student in senior class for excellence in computer science.
		\item Research Experience Scholars Program -- Artificial Intelligence Research in Kaiserslautern, Germany. %NOLINT
	\end{itemize}}

\section{Experience}
\cventry{2017--present}{Unpaid Research Intern under Ioannis Rekleitis}{Autonomous Field Robotics Laboratory, USC}{Columbia, SC}{}{Internship conducting research dealing with the cooperative localization of underwater robots using computer vision. \\ Work being prepared for iROS 2018 conference.}

\cventry{Summer 2016}{Research Intern under Marco Hirsch}{German Research Center for Artificial Intelligence (DKFI)}{Kaiserslautern, Germany}{}{Internship developing a non-linear method of administering questionnaires for improved efficiency. \\ Wrote unpublished paper: ``Structured Representation for Dynamic Survey Logic''}

\cventry{2016--2017}{Cofounder, Software Developer}{Calendry Technologies}{Hartsville, SC}{}{Helped start Calendry Technologies and its GoHartsville Project to consolidate information about community events from multiple sources into one calendar using an automated system.}

\section{Relevant Coursework}
\subsection{\textbf{University of South Carolina}\dotfill}
\cvitem{Computer Science}{Digital Systems, Linux, Bash Scripting, (In Progress: Software Engineering, Computer Architecture, Assembly Language)}
\cvitem{Mathematics}{Vector Calculus, Transition to Advanced Mathematics, (In Progress: Linear Algebra, Discrete Mathematics)}
\subsection{\textbf{SC Governor's School for Science and Mathematics}\dotfill}
\cvitem{Computer Science}{Linux, C/C++, Java, Python, ROS, Computer Vision, Localization/Mapping, Machine Learning, Game Design}
\cvitem{Mathematics}{Abstract Algebra, Single Variable Calculus, Numerical Integration}
\end{document}
